Automatic Identification and Annotation of Parallel Tasks in Structured Programs

### 2017-11-05 docs/ACM/paper.tex
Adding references to Tareador.

Annotation systems have risen to a place of prominence as a simple and
effective way to write parallel programs.
Examples of such systems include OpenMP~\cite{JaegerCP15},
OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10} and OpenSs~\cite{MeenderinckJ11}.
Annotations work as a meta-language: they let developers grant parallel
semantics to syntax originally written to execute sequentially.
The compiler-related literature contains a generous load of success stories
describing the use of annotation systems to parallelize programs.
Combined with modern accelerators, they have led to substantial performance
gains~\cite{Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
Yet, even if convenient, the use of annotations is not straightforward, and
lacks supporting tools.

Annotations such as OpenMP or OpenACC still require developers to
worry about typical hassles of the parallel world, such as race conditions
or deadlocks.
Moreover, because they are used in tandem with imperative programming languages,
such troubles are only made worse by pointer aliasing.
There exist tools that insert automatic annotations in
programs~\cite{gleison2016,Pingali11,wanggenerating}.
All these technologies explore data-parallelism -- the possibility of running
the same computation independently on different data.
Task parallelism remains still uncharted land, in what concerns automatic
annotation.
Such fact is unfortunate, because much of the power of current annotation
systems lays on their ability to create tasks \ed{We need to find references!}.
This ability brings said systems closer to irregular programs such as those
that implement graphs and worklist algorithms \`{a} la
Pingali~\cite{Ben-Nun17,Kulkarni11,Pingali11}.
The goal of this work is to address this omission.

>>>>

Annotation systems have risen to a place of prominence as a simple and
effective way to write parallel programs.
Examples of such systems include OpenMP~\cite{JaegerCP15},
OpenACC~\cite{OpenACC20}, OpenHMPP~\cite{Andion14}, OpenMPC~\cite{Lee10},
OpenSs~\cite{MeenderinckJ11} and Tareador~\cite{Ayguade15}.
Annotations work as a meta-language: they let developers grant parallel
semantics to syntax originally written to execute sequentially.
The compiler-related literature contains a generous load of success stories
describing the use of annotation systems to parallelize programs.
Combined with modern accelerators, they have led to substantial performance
gains~\cite{Bertolli14,Mendonca17,Poesia17,Reyes12,Wienke12}.
Yet, even if convenient, the use of annotations is not straightforward, and
lacks supporting tools.

Annotations such as OpenMP or OpenACC still require developers to
worry about typical hassles of the parallel world, such as race conditions
or deadlocks.
Moreover, because they are used in tandem with imperative programming languages,
such troubles are only made worse by pointer aliasing.
There exist tools that insert automatic annotations in
programs~\cite{Mendonca16,Pingali11,Nugteren14}.
All these technologies explore data-parallelism -- the possibility of running
the same computation independently on different data.
Task parallelism remains still uncharted land, in what concerns automatic
annotation.
Such fact is unfortunate, because much of the power of current annotation
systems lays on their ability to create tasks \ed{We need to find references!}.
This ability brings said systems closer to irregular programs such as those
that implement graphs and worklist algorithms \`{a} la
Pingali~\cite{Ben-Nun17,Kulkarni11,Pingali11}.
The goal of this work is to address this omission.
